Time--Frequency Scattering Accurately Models Auditory Similarities Between Instrumental Playing Techniques

### 2020-11-01 paper/paper.tex
cite caetano
cite siedenburg 2019 jasa

Moreover, a quantitative benchmark over Medley-solos-DB has demonstrated that joint time--frequency scattering, unlike purely temporal scattering, outperforms deep convolutional networks in supervised musical instrument classification, even in a relatively large data regime with 500 to 5k samples per class \cite{anden2019tsp}. % \ja wants 5,000
However, it remains to be seen whether joint time--frequency scattering is capable of fine-grained auditory categorization, involving variability in instrument, mute, and playing technique.
In addition, previous publications on joint time--frequency scattering lack a human-centric evaluation, independently from any classification task.

@@

>>>>

Moreover, a quantitative benchmark over Medley-solos-DB has demonstrated that joint time--frequency scattering, unlike purely temporal scattering, outperforms deep convolutional networks in supervised musical instrument classification, even in a relatively large data regime with 500 to 5k samples per class \cite{anden2019tsp}. % \ja wants 5,000
However, it remains to be seen whether joint time--frequency scattering is capable of fine-grained auditory categorization, involving variability in instrument, mute, and playing technique.
In addition, previous publications on joint time--frequency scattering lack a human-centric evaluation, independently from any classification task.
Beyond the case of STRF, we refer to \cite{caetano2019chapter} for a detailed review of the state of the art on audio descriptors of timbre.

@@

These findings are in line with a previous publication \cite{patil2012ploscompbiol} which modeled perceived dissimilarity between musical sounds by means of STRF features.
Likewise, a recent publication has observed similar performance in instrument identification of a human and machine classifier using separable Gabor filterbank (GBFB) features \cite{siedenburg2019jasa}.
We note that both STRF and GBFB bear a strong computational resemblance with time--frequency scattering.
